### 2023-09-01 paper/sec-results.tex
updated event rate to table

\paragraph{FASER$\nu$2 compared to AdvSND and FLArE.}
%
In addition to FASER$\nu$2, we have also produced PDF impact projections for
other proposed FPF experiments, specifically for AdvSND and FLArE.
%
In the latter case, we consider both the 10 ton and 100 ton variants.
%
Figs.~\ref{fig:FASERnu2_advsnd} and~\ref{fig:FASERnu2_FLAre10} compare the PDF sensitivity
of FASER$\nu$2, in the scenario where systematic uncertainties are neglected, with the corresponding
results for AdvSND and FLArE100 respectively.
%
As summarised by Table~\ref{tab:integrated_rates}, each of these experiments
has associated different expected numbers of DIS events, namely 370k, 43k, and 81k (420K)
inclusive muon-neutrino events for FASER$\nu$2, AdvSND and FLArE10~(100) respectively,
with 57k, 4.5k, and 11k (59k) in the charm-tagged case.
%
In this comparison, one would expect that experiments with the largest event rates best PDF sensitivity.

>>>>

\paragraph{FASER$\nu$2 compared to AdvSND and FLArE.}
%
In addition to FASER$\nu$2, we have also produced PDF impact projections for
other proposed FPF experiments, specifically for AdvSND and FLArE.
%
In the latter case, we consider both the 10 ton and 100 ton variants.
%
Figs.~\ref{fig:FASERnu2_advsnd} and~\ref{fig:FASERnu2_FLAre10} compare the PDF sensitivity
of FASER$\nu$2, in the scenario where systematic uncertainties are neglected, with the corresponding
results for AdvSND and FLArE100 respectively.
%
As summarised by Table~\ref{tab:integrated_rates}, each of these experiments
has associated different expected numbers of DIS events, namely 260k, 28k, and 57k (340K)
inclusive muon-neutrino events for FASER$\nu$2, AdvSND and FLArE10~(100) respectively,
with 39k, 3.5k, and 7.7k (45k) in the charm-tagged case.
%
In this comparison, one would expect that experiments with the largest event rates best PDF sensitivity.
